weight_analyses

### 2022-10-26 smelt_2019_winterspring/manuscript_weight_length_k_survival.Rmd
minor change to survival table, publishing format

# ----------------Rio Vista-----------------------------------------
# Calculate sample sizes for alive and dead
surv_RV <- Cagetype_s %>%
  filter(Site == "RV") %>%
  group_by(Site, Cage, Mesh)%>%
  summarize(
    Alive = n(),
    Dead = 64-n()
  ) %>%
  mutate(rate = Alive/(Alive + Dead)*100)

# Create data frame of each individual fish - survived or did not survive
Cage_survival_RV <- as.data.frame(matrix(0, ncol = 2, nrow = 384))
colnames(Cage_survival_RV) <- c("Cage", "Survived")

@@

Cagetype_survival_RV <- Cagetype_survival_RV %>%
  mutate(Cage = factor(Cage),
         Survived = factor(Survived),
         Site = factor(Site),
         Mesh = factor(Mesh))
```

@@

### DWSC
```{r}

surv_DWSC <- Cagetype_s %>%
  filter(Site == "DWSC") %>%
  group_by(Site, Cage, Mesh)%>%
  summarize(
    Alive = n(),
    Dead = 60-n()
  ) 
# Add dead fish
  # Add NTF4 to dead in Cage F - "decomposed"
  # Add RB61 to dead in Cage F - "partly decomposed"

@@

Cagetype_survival_DWSC <- Cagetype_survival_DWSC %>%
  mutate(Cage = factor(Cage),
         Survived = factor(Survived),
         Site = factor(Site),
         Mesh = factor(Mesh))%>%
  mutate(rate = Alive/(Alive + Dead)*100)
```

>>>>

# ----------------Rio Vista-----------------------------------------
# Create data frame of each individual fish - survived or did not survive
Cage_survival_RV <- as.data.frame(matrix(0, ncol = 2, nrow = 384))
colnames(Cage_survival_RV) <- c("Cage", "Survived")

@@

survival_RV <- Cagetype_survival_RV %>%
   mutate(Cage = factor(Cage),
         fSurvived = factor(Survived),
         Survived = as.numeric(Survived),
         Site = factor(Site),
         Mesh = factor(Mesh))%>%
  group_by(Mesh, Cage) %>%
  summarize(Survived = sum(Survived),
            n= n()) %>%
  mutate(rate = Survived/n*100)
```

@@

### DWSC
```{r}
# Add dead fish
  # Add NTF4 to dead in Cage F - "decomposed"
  # Add RB61 to dead in Cage F - "partly decomposed"

@@

survival_DWSC <- Cagetype_survival_DWSC %>%
  mutate(Cage = factor(Cage),
         fSurvived = factor(Survived),
         Survived = as.numeric(Survived),
         Site = factor(Site),
         Mesh = factor(Mesh))%>%
  group_by(Mesh, Cage) %>%
  summarize(Survived = sum(Survived),
            n= n()) %>%
  mutate(rate = Survived/n*100)
```

EDI table for survival
```{r}
survival_bind <- rbind(survival_DWSC, survival_RV) %>%
  mutate(rate = round(rate,2))
write_csv(survival_bind, here::here("smelt_2019_winterspring", "data_clean", "2019_smeltstudy_survival_data.csv"))
```
